Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-03-15 apples_and_oranges.qmd
Test

df_overall_baseline_results %>%
  kbl(align = "l", caption = "Table 1: Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

@@

df_sites_summary_stats %>%
  kbl(caption = "Table X: Number of sites across medication and psychotherapy studies") %>% 
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

@@

sites_t_test_stats %>%
  kbl(align = "l", caption = "Table X: Results for t-test comparing number of sites between medication and psychotherapy studies") %>% 
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

@@

df_mean_coefs_from_sim %>%
  kbl(align = "l", caption = "Table X: Summary statistics of the estimated SMDs") %>% 
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

@@

aggregate_results_overall %>%
  kbl(caption = "Table X: Meta-regression results") %>% 
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

@@

control_summary %>%
  kbl(align = "l", caption = "Table X: Comparing the intensity of the intervention between active and control arms of psychotherapy studies", escape = F) %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  column_spec(1, border_right = T) %>% 
  pack_rows("Number of sessions", 1, 2) %>% 
  pack_rows("Frequency (weeks)", 3, 4) %>% 
  pack_rows("Session length (mins)", 5, 6) %>%
  pack_rows("Total intervention hours", 7, 8) %>%
  pack_rows("Total intervention period (weeks)", 9, 10)

@@

control_summary_t_tests %>%
  kbl(align = "l", caption = "Table X: Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials") %>% 
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

@@

df_severity_sens %>%
  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials", escape = F) %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

@@

df_gender_sens %>%
  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials", escape = F) %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

@@

df_age_sens %>%
  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of age between psychotherapy and medication trials", escape = F) %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

>>>>

df_overall_baseline_results %>%
  kbl(align = "l", caption = "Table 1: Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

@@

df_sites_summary_stats %>%
  kbl(caption = "Table X: Number of sites across medication and psychotherapy studies") %>% 
  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

@@

sites_t_test_stats %>%
  kbl(align = "l", caption = "Table X: Results for t-test comparing number of sites between medication and psychotherapy studies") %>% 
  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

@@

df_mean_coefs_from_sim %>%
  kbl(align = "l", caption = "Table X: Summary statistics of the estimated SMDs") %>% 
  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

@@

aggregate_results_overall %>%
  kbl(caption = "Table X: Meta-regression results") %>% 
  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

@@

control_summary %>%
  kbl(align = "l", caption = "Table X: Comparing the intensity of the intervention between active and control arms of psychotherapy studies", escape = F) %>%
  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  column_spec(1, border_right = T) %>% 
  pack_rows("Number of sessions", 1, 2) %>% 
  pack_rows("Frequency (weeks)", 3, 4) %>% 
  pack_rows("Session length (mins)", 5, 6) %>%
  pack_rows("Total intervention hours", 7, 8) %>%
  pack_rows("Total intervention period (weeks)", 9, 10)

@@

control_summary_t_tests %>%
  kbl(align = "l", caption = "Table X: Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials") %>% 
  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

@@

df_severity_sens %>%
  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials", escape = F) %>%
  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

@@

df_gender_sens %>%
  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials", escape = F) %>%
  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

@@

df_age_sens %>%
  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of age between psychotherapy and medication trials", escape = F) %>%
  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
